Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

The content loss $L_\text{content}$ is the easier one to explain of the two losses.
It is the mean square error between the outputs of a certain function in the
vgg19 taking the current argument image and the content image as inputs respectively.
We say ``a certain'' function because the output of which function to choose is
adjustable.
A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
\begin{figure}
\center
\includegraphics[width=\textwidth]{contentloss.pdf}
\caption{The content loss $L_{content}$ \label{contentloss}}
\end{figure}

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are,
for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.

Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived \verb|conv_1| and \verb|conv_4| in Figure $\ref{stylelosses}$.

\begin{figure}
\center
\includegraphics[width=\textwidth]{stylelosses}
\end{figure}

@@

However, could we achieve the same results with other

@@

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{method}
Gedeon, T.D. and Harris, D. (1991) "Network Reduction Techniques," Proceedings International Conference on Neural Networks Methodologies and Applications, AMSE, San Diego, vol. 1: 119-126. 
\bibitem{prune0}
Penington, Jocelyn \& Dow, R.J.F.. (1988). Neural net pruning—Why and how. Proceedings of the IEEE Conference on Neural Networks. 1. 325 - 333 vol.1. 10.1109/ICNN.1988.23864. 
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{example_prune}
Han, S., Mao, H., \& Dally, W.J. (2016). Deep Compression: Compressing Deep Neural Network with Pruning, Trained Quantization and Huffman Coding. CoRR, abs/1510.00149.
\bibitem{example_simplification}
Sun, X., Ren, X., Ma, S., Wei, B., Li, W., \& Wang, H. (2018). Training Simplification and Model Simplification for Deep Learning: A Minimal Effort Back Propagation Method. CoRR, abs/1711.06528.
\bibitem{example_compression}
Cheng, Yu \& Wang, Duo \& Zhou, Pan \& Zhang, Tao. (2017). A Survey of Model Compression and Acceleration for Deep Neural Networks. 
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}

>>>>

The content loss $L_\text{content}$ is the easier one to explain of the two losses.
It is the mean square error between the outputs of a certain function in the
vgg19 taking the current argument image and the content image as inputs respectively.
We say ``a certain'' function because the output of which function to choose is
adjustable.
A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
\begin{figure}
\center
\includegraphics[width=\textwidth]{contentloss.pdf}
\caption{The content loss \label{contentloss}}
\end{figure}

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are,
for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.
Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.

\begin{figure}
\center
\includegraphics[width=\textwidth]{styleloss.pdf}
\caption{The style loss derived from the output of conv\_1 \label{styleloss}}
\end{figure}

@@

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitute. 
For us, it seemed more natural to consider substitute to the process of 
transforming feature maps to Gram matrices itself, that is, 
a mapping that removes the spatial information of where features are but retains
the distribution of features like a histogram.

@@

\subsection{Varying the dislocator function}

\subsection{Varying the extraction points for losses}

We will also show that other factors, such that the outputs of which functions to derive the style 
losses from are not very essential and somewhat belongs to tuning.

@@

\begin{thebibliography}{8}
\bibitem{nst}
Gatys, L., Ecker, A., \& Bethge, M. (2016). A neural algorithm of artistic style. Journal of Vision, 16(12), 326. doi:10.1167/16.12.326
\bibitem{demyst}
Li, Y., Wang, N., Liu, J., \& Hou, X. (2017). Demystifying Neural Style Transfer. IJCAI.
\bibitem{interp}
Doshi-Velez, F., \& Kim, B. (2017). Towards A Rigorous Science of Interpretable Machine Learning.
\bibitem{pytorch}
Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., Lin, Z., Desmaison, A., Antiga, L., \& Lerer, A. (2017). Automatic differentiation in PyTorch.
\end{thebibliography}
\end{document}
